---
title: "Bi-Directional Bindings"
author: "Janko Thyson"
date: "Thursday, October 16, 2014"
output: pdf_document
---

```{r, echo=FALSE}
suppressMessages(require("reactr"))
```

## Scenario 1: use references "as is" (no functional transformation/processing)

### Scenario explanation

- Type/Direction: 

  `A` references `B` and `B` references `A` --> bidirectional binding type
  
- Binding/Relationship: 

  `A` uses value of `B` "as is" and `B` uses value of `A` "as is". This results in a **steady state**. 

### Example

A cool feature of this binding type is that you are free to alter the values of *both* objects and still keep everything "in sync"

```{r}
setReactiveS3(id = "x_1", function() "object-ref: {id: x_2}")
setReactiveS3(id = "x_2", function() "object-ref: {id: x_1}")
```

Note that the call to `setReactiveS3()` merely initializes objects with bidirectional bindings to the value `numeric(0)`:

```{r}
x_1

x_2
```

You must actually assign a value to either one of them via `<-` **after** establishing the binding:

```{r}
## Set actual initial value to either one of the objects //
(x_1 <- 100)
x_2
x_1

## Changing the other one of the two objects //
(x_2 <- 1000)
x_1
```

Clean up

```{r, echo=FALSE}
rmReactive("x_1")
rmReactive("x_2")
```

## Scenario 2: use functionally transformed/process value (steady state)

### Scenario explanation

- Type/Direction: 

  `A` references `B` and `B` references `A` --> bidirectional binding type
  
- Binding/Relationship: 

  `A` uses transformed value of `B` and `B` uses transformed value of `A`. 
  
  The binding functions used result in a **steady state**.

### Example

As the binding functions are "inversions"" of each other, we still get to a steady state.

```{r}
setReactiveS3(id = "x_1", function() {
  "object-ref: {id: x_2}"
  x_2 * 2
})

setReactiveS3(id = "x_2", function() {
  "object-ref: {id: x_1}"
  x_1 / 2
})
```

Note that due to the structure of the binding functions, the visible object values are initialized to `numeric()` instead of `NULL` now.

```{r}
x_1
x_2
```

Here, we always reach a steady state, i.e. a state in which cached values can be used instead of the need to executed the binding functions.

```{r}
## Set actual initial value to either one of the objects //
(x_1 <- 100)
x_2
x_1

## Changing the other one of the two objects //
(x_2 <- 1000)
x_1
x_2
```

Clean up

```{r, echo=FALSE}
rmReactive("x_1")
rmReactive("x_2")
```

## Scenario 3: use functionally transformed/process values (no steady state)

### Scenario explanation

- Type/Direction: 

  `A` references `B` and `B` references `A` --> bidirectional binding type
  
- Binding/Relationship: 

  `A` uses transformed value of `B` and `B` uses transformed value of `A`. 
  
  The binding functions used result in a **non-steady state**.

### Example

As the binding functions are **not** "inversions"" of each other, we never reach/stay at a steady state. Cached values are/can never be used as by the definition of the binding functions the two objects are constantly updating each other.

```{r}
setReactiveS3(id = "x_1", function() {
  "object-ref: {id: x_2}"
  x_2 * 2
})

setReactiveS3(id = "x_2", function() {
  "object-ref: {id: x_1}"
  x_1 * 10
})
```

Here, we have "non-steady-state" behavior, i.e. we never reach a state were cached values can be used. We always need to execute the binding functions as each request of a visible object value results in changes. 

This is best verified when using `verbose = TRUE` and comparing it to the other scenarios (not done at this point).

```{r}
x_1
x_2

## Set actual initial value to either one of the objects //
(x_1 <- 1)

x_2
## --> `x_1` * 10

x_1
## --> x_2 * 2

x_2
## --> `x_1` * 10

## Changing the other one of the two objects //
(x_2 <- 1)
x_1
x_2
x_1
```

Clean up 

```{r, echo=FALSE}
rmReactive("x_1")
rmReactive("x_2")
```

