---
title: "Convenience Functions"
author: "Janko Thyson"
date: "Thursday, October 29, 2014"
output:
  pdf_document
---

```{r, echo=FALSE}
suppressMessages(require("reactr"))
```

## Reactive objects (focus *visible* part)

Example objects

```{r}
setReactive(id = "x_1", value = 10)
setReactive(id = "x_2", value = function() "object-ref: {id: x_1}")
```

### Compute object UID

```{r}
computeObjectUid(id = "x_1")
computeObjectUid(id = "x_2")
```


### Copy reactive objects

```{r}
copyReactive(id_from = "x_1", id_to = "x_1_copy")
x_1_copy
```

### Get reactive

```{r}
getReactive(id = "x_1")
getReactive(id = "x_1", hidden = TRUE)
getReactive(id = "x_2")
```

### Is reactive 

```{r}
isReactive(id = "x_1")
isReactive(id = "x_2")
x_3 <- "hello world!"
isReactive(id = "x_3")
```

## Unset reactive

```{r}
unsetReactive(id = "x_1")
isReactive(id = "x_1")
```

## Removing reactive 

```{r}
rmReactive(id = "x_1")
exists("x_1")
## --> already unset
rmReactive(id = "x_2")
exists("x_2")
```

## Reactive objects (focus *invisible* part)

Example objects 

```{r}
setReactive(id = "x_1", value = 10)
setReactive(id = "x_2", value = function() {
  "object-ref: {id: x_1}"
  x_1 * 2
})
```


### Get binding function

```{r}
getBinding(id = "x_1")
getBinding(id = "x_2")
```

### Get checksum of visible value

```{r}
getChecksum(id = "x_1")
getChecksum(id = "x_2")
```

### Get reactive 

```{r}
getReactive(id = "x_1", hidden = TRUE)
getReactive(id = "x_2", hidden = TRUE)
```

### Show pull references

```{r}
showPullRefs(id = "x_1")
showPullRefs(id = "x_2")
```

### Show push references

```{r}
showPushRefs(id = "x_1")
showPushRefs(id = "x_2")

setReactive(id = "x_2", value = function() {
  "object-ref: {id: x_1}"
  x_1 * 2
}, push = TRUE)
showPushRefs(id = "x_2")
```

Clean up 

```{r}
rmReactive("x_1")
rmReactive("x_2")
```

## Registry

Example objects 

```{r}
setReactive(id = "x_1", value = 10)
setReactive(id = "x_2", value = function() "object-ref: {id: x_1}")
```

### Get registry 

```{r}
reg <- getRegistry()
ls(reg)
```

### Show registry

```{r}
showRegistry()
```

### Get from registry

```{r}
getFromRegistry(id = "x_1")
getFromRegistry(id = "x_2")

getFromRegistryByUid(computeObjectUid("x_1"))
getFromRegistryByUid(computeObjectUid("x_2"))
```

### Remove from registry

```{r}
computeObjectUid("x_1") %in% showRegistry()
rmFromRegistry("x_1")
computeObjectUid("x_1") %in% showRegistry()

computeObjectUid("x_2") %in% showRegistry()
rmFromRegistryByUid(computeObjectUid("x_2"))
computeObjectUid("x_2") %in% showRegistry()
```

### Reset registry 

```{r}
## Ensure content that might previously have been removed //
setReactive(id = "x_1", value = 10)
setReactive(id = "x_2", value = function() "object-ref: {id: x_1}")

## Reset //
showRegistry()
resetRegistry()
showRegistry()
```

