---
title: "Pushing"
author: "Janko Thyson"
date: "Thursday, October 29, 2014"
output:
  pdf_document
---

```{r, echo=FALSE}
suppressMessages(require("reactr"))
```

**NOT FINISHED YET**

The underlying registry mechanism of `reactr` ensures that **references** of the invisible instances/objects of class [ReactiveObject.S3](../R/ReactiveObject.S3) or [ReactiveShinyObject](../R/ReactiveShinyObject) are stored in a registry object (see vignette [Registry](./registry.pdf) for details). 

Besides being a prerequisite for the caching mechanism that allows the specification of bi-directional bindings (see vignette [Bi-Directional Bindings](./bidirectional_bindings.pdf), this also facilitates the use of a **push paradigm** with respect to reactivity or the way that object state changes are propagation throughout the system.

Below is a short example that illustrates how the push mechanism works.

## Scenario description

We set up a very simple example:

- there exists a reactive object that other objects can reference: `x_1`
- each modification of `x_1` should trigger two events in a **push** manner:

    1. Update a database table
    2. Send an E-Mail to a certain address

## Implementation

Ensure that required packages are loaded

```{r, message=FALSE}
pkgs <- c("dplyr", "sendmailR", "RSQLite", "sqldf")
. <- sapply(pkgs, function(pkg) {
  if (!suppressWarnings(require(pkg, character.only = TRUE))) {
    install.packages(pkg)
    require(pkg, character.only = TRUE)
  }
  invisible(NULL)
})

```

Create reactive object that others can reference:

```{r}
setReactiveS3(id = "x_1", value = 1)
```
 
Define the actual core functions for 

- the database update
- sending the E-Mail
  
 
```{r}
updateDatabase <- function(
  id, 
  value, 
  con = file.path(tempdir(), "testdb.sqlite")
) {
  my_db <- src_sqlite(path = con, create = TRUE)
  
#   dbRemoveTable(db, id)
  this <- data.frame(time = as.character(Sys.time()), value = value)
  if (!id %in% dbListTables(my_db$con)) {
    copy_to(my_db, this, id, temporary = FALSE) # need to set temporary to FALSE 
  }
    
  sql <- sprintf(
    'INSERT INTO %s VALUES (%s, %s)', 
    id, paste0("\"", Sys.time(), "\""), value
  )
  dbSendQuery(my_db$con, sql)
#   dbReadTable(my_db$con, id)
  message("Updated database")
  TRUE
}

sendEmail <- function(id, value, con) {
  
}
```

Database connection settings

```{r}
con <- file.path(tempdir(), "testdb.sqlite")
my_db <- src_sqlite(path = con, create = TRUE)
try(dbReadTable(my_db$con, "x_1"), silent = TRUE)
```

Push in action 

```{r}
setReactiveS3(
  id = "pushToDatabase", 
  value = function() {
    "object-ref: {id: x_1}"
    updateDatabase(
      id = "x_1", 
      value = x_1,
      con = file.path(tempdir(), "testdb.sqlite")
    )
    TRUE
  }, 
  push = TRUE
)

x_1 <- 2
x_1 <- 3
x_1 <- 4
x_1 <- 5

## Inspect database //
dbReadTable(my_db$con, "x_1")
```

Note that we never explicitly called `pushToDatabase`.

It was called whenever `x_1` changed.

Clean up 

```{r, message=FALSE}
rmReactive("x_1")
rmReactive("x_2")
```

