---
title: "Registry"
author: "Janko Thyson"
date: "Thursday, October 29, 2014"
output: 
  pdf_document
---

```{r, echo=FALSE}
suppressMessages(require("reactr"))
resetRegistry()
```

Whenever a reactive object is set via `setReactiveS3()`, the object that is *actually* created is an instance of class `ReactiveObject.S3` even though it does not appear so: the instance itself remains invisible and only the value of its field `value` is made visible to the user/system and can thus subsequently be accessed and manipulated through the name/ID provided in `id` in the call to `setReactiveS3()`

```{r}
setReactiveS3(id = "x_1", 10)
x_1
class(x_1)
```

Usually, due to the way `makeActiveBinding()` works, we would not be able to access this hidden object once the function returns as it is only stored internally. In order to keep the object accessible, `setReactiveS3()` stores it in an internal registry.

The registry can be accessed via 

```{r}
getOption("reactr")$.registry
```

or via the convenience function `getRegistry()`

```{r}
registry <- getRegistry()
```

As mentioned, the actual content consists of the respective **invisible** objects that were created in the call to `setReactiveS3()` which are assigned to names that correspond to the UIDs of its **visible** parts

```{r}
ls(registry)
```



```{r}
x_1_hidden <- getFromRegistry(id = "x_1")
x_1_hidden
class(x_1_hidden)
```



